% 10.2pt
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{url}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
% -.5in
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \textlf{Related courses: #5}
}

\newcommand{\experienceSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Xiaotan Zhu}} & Email : \href{mailto:sugarmanzhu@gmail.com}{sugarmanzhu@gmail.com}\\
  \url{https://zhuxiaotan.com/} & WhatsApp : +44 7410078526 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dulwich International High School Suzhou}{Suzhou, China}
      {A Level;  A*A*A*A*}{Sep. 2014 - Jul. 2018}
      {Further Mathematics, Mathematics, Physics, Computer Science, Chemistry, Economics}
    \resumeSubheading
      {The University of Manchester}{Manchester, UK}
      {Bachelor of Computer Science;  First Class}{Sep. 2018 - Jul. 2021}
      {Algorithms and Complexity, Documents and Data on the Web, Cryptography and System Security, AI and Games, The Internet of Things: Architectures and Applications, Cognitive Robotics, Computer Vision}
    \resumeSubheading
      {Imperial College London}{London, UK}
      {Masters in Advanced Computing;  Merit}{Oct. 2021 - Oct. 2022}
      {Mathematics for Machine Learning, Reinforcement Learning, Introduction to Machine Learning, Computational Finance, Computer Vision, Network and Web Security, Cryptography Engineering, Deep Learning, Principles of Distributed Ledgers, Robot Learning and Control}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
	\resumeSubHeadingListStart
    \resumeSubItem{Human Languages}{English, Chinese}
	\resumeSubItem{Programming Languages}{Python, Java, Javascript, Typescript, HTML, CSS/SASS}
	\resumeSubItem{Tools}{Git, Docker, Jupyter Notebook, NumPy, Pytorch, VS Code, React, Nginx, Apache, AWS, VueJS, NextJS}
    \resumeSubItem{Operating Systems}{Windows, MacOS, Linux}
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \experienceSubheading
    {Meezao.com}{Beijing, China}
    {Software Engineer Internship}{Jul. 2019 - Sep. 2019}
    \resumeItemListStart
        \resumeItem{Client Web Interface}
          {Linked databases to the user interface, and ECharts was used to present the data. Redesigned user interface with a mobile-friendly and readable layout.}
          \resumeItem{Application Features}
          {Changed the user interface to facilitate looking up historical data and real-time updates.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACADEMIC PROJECTS-----------------
\section{Academic Projects}
\resumeSubHeadingListStart
\resumeSubItem{Verifying Learned Rewards}{Reproduced findings from the research "Deep RL from Human Preferences" which models human preferences using deep neural networks. Provided some solutions after analysing the learnt reward models' shortcomings and limits. Participated in the GitHub imitation project.}
\resumeSubItem{Deep Q-Learning Project}{Utilized reinforcement methods like Double DQN, Dueling DQN, Prioritized Experience Replay to create an agent that can play Super Mario Bros at a human expert level with only pixel input.}
\resumeSubHeadingListEnd

%-----------PERSONAL PROJECTS-----------------
\section{Personal Projects}
\resumeSubHeadingListStart
\resumeSubItem{Personal Website (\url{https://zhuxiaotan.com})}{My NextJS-based web portfolio. The website features a clean and modern design, making it easy to navigate and explore the various sections. The project is open sourced at \url{https://github.com/SugarmanZhu/Portfolio_Vercel}}
\resumeSubItem{Emby Media Project (\url{https://emby.zhuxiaotan.com})}{An automatic media server with Emby. The project searches TMDb and Douban for popular content, extracts their metadata, organises the content into categories, and then displays it on Emby. Guest Account Username: Guest, Password: PublicAccess}
\resumeSubItem{RSS Reader (\url{https://rss.zhuxiaotan.com})}{A RSS project based on NextJS. For the purpose of tracking all of its content in one location, the website integrates RSS feeds from various sources. Additionally, the project offers an API for retrieving RSS feeds. The project is open sourced at \url{https://github.com/SugarmanZhu/RSS_Vercel}}
\resumeSubItem{Reaction Test (\url{https://reaction-time.zhuxiaotan.com})}{A straightforward website to test response time. The project is based on VueJS and is open sourced at \url{https://github.com/SugarmanZhu/Reaction_Time_Vercel}}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStart
\resumeSubItem{AWS Certified Cloud Practitioner}{\url{https://www.credly.com/badges/5c5c2ea7-584f-488c-b38d-eb9540337af7/linked_in_profile}}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
